Allele Frequencies Common Gardens

### 2020-01-24 analysis/common-garden-allele-balancing/2_allele_frequencies_common_gardens.Rmd
Clarify analysis in Rmd file

##

```{r}
load("~/Github/pvdiv-phenology-gxe/data/sites.rda")
```

```{r}
year <- "2019"
i=1
k= i+1
nmax = 33890000

@@

@@

@@

# 36007 out of 100k sites had MAF > 0.05 at Pickle in 2018, our best site.
12.2M SNPs total.
# 28544 out of 100k sites have MAF > 0.05 at all 10 locations.
That's 7463 SNPs less, or 79.27% of the SNPs we would have had.
9.67M SNPs total. Lose 20% of the SNPs by constraining to 5% MAF at all sites.

@@

@@

@@

# Plots

>>>>

# Join data on server

```{r}
load("~/Github/pvdiv-phenology-gxe/data/sites.rda")
year <- "2019"
i=1
k= i+1
nmax = 33890000

@@

## Load data

@@

## Tally SNPs by site

@@

    *36007 out of 100k sites had MAF > 0.05 at Pickle in 2018, our best site.
    *12.2M SNPs total.
    *28544 out of 100k sites have MAF > 0.05 at all 10 locations.

That's 7463 SNPs less, or 79.27% of the SNPs we would have had.
9.67M SNPs total. Lose 20% of the SNPs by constraining to 5% MAF at all sites.

@@

# ------------------
# Start of Plots

@@

## Labeled hex plots

@@

## Grid of plots?
